Supplement 2: Stationwise Evaluation

### 2018-09-22 pkg/disttree/inst/draft/supplement/supplement_stationwise.Rnw
revised versions of supplements with corresponding reproduction files
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2289 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 443c37f89e7b5b3420a6e5a3862fb100989d9f2d

%\subsection{Subset selection}
The models are always learned on data from 24 years and tested on the 
remaining 4 years. Splitting the data into these two subsets has been done
in two different ways leading to the two following evaluation settings.
%
\begin{itemize}

@@

\subsection{Forecasting skills} 
Comparing CRPS values of the single split setting it can be stated that the forest model works well over all stations. Often it is even the best performing method (e.g. at stations \hyperlink{sumLech.1}{Lech}, \hyperlink{sumSeeimPaznaun.1}{See im Paznaun} and \hyperlink{sumGinzling.1}{Ginzling}), but there are also stations where one of the other models leads to better results. For example at \hyperlink{sumOchsengartenObergut.1}{Ochsengarten-Obergut} the boosted GAMLSS performs best, at \hyperlink{sumRotholz.1}{Rotholz} the EMOS model and at \hyperlink{sumMatreiinOsttirol.1}{Matrei in Osttirol} the prespecified GAMLSS is the best model, however, they do not clearly outperform the forest model. Moreover, these advantages often even out or turn into disadvantages when looking at the CRPS values from the cross-validation. For example at station \hyperlink{sumInnervillgraten.1}{Innervillgraten}, the prespecified GAMLSS is clearly the best in the single split setting, however, in the cross-validation the forest model is slightly ahead. An exception is given by station \hyperlink{sumSt.JohannimWalde.1}{St.Johann im Walde} as it is the only station where the prespecified GAMLSS clearly outperforms all other models in both settings. But overall, the results from the cross validation also support the statement that the forest model performs well on all stations being either the best or among the best performing methods at the majority of stations.
Moreover, it can be concluded that Axams is an observation station without any unusual features that would lead to outstanding performances of any of the methods. Therefore, it is a reasonable choice as a representative for all 95 station. Examples for stations where the forest model performs better or worse can be found easily, however, in general the methods perform similarly as for station Axams.

>>>>

%\subsection{Subset selection}
The models are always learned on data from 24 years and tested on the 
remaining 4 years. Splitting the data into these two subsets is done
in two different ways leading to the two following evaluation settings.
%
\begin{itemize}

@@

\subsection{Forecasting skills} 
Comparing CRPS values of the single split setting it can be stated that the forest model works well over all stations. Often it is even the best performing method (e.g. at stations \hyperlink{sumLech.1}{Lech}, \hyperlink{sumSeeimPaznaun.1}{See im Paznaun} and \hyperlink{sumGinzling.1}{Ginzling}), but there are also stations where one of the other models leads to better results. For example at \hyperlink{sumOchsengartenObergut.1}{Ochsengarten-Obergut} the boosted GAMLSS performs best, at \hyperlink{sumRotholz.1}{Rotholz} the EMOS model and at \hyperlink{sumMatreiinOsttirol.1}{Matrei in Osttirol} the prespecified GAMLSS is the best model, however, they do not clearly outperform the forest model. Moreover, these advantages often even out or turn into disadvantages when looking at the CRPS values from the cross-validation. For example at station \hyperlink{sumInnervillgraten.1}{Innervillgraten}, the prespecified GAMLSS is clearly the best in the single split setting, however, in the cross-validation the forest model is slightly ahead. An exception is given by station \hyperlink{sumSt.JohannimWalde.1}{St.Johann im Walde} as it is the only station where the prespecified GAMLSS clearly outperforms all other models in both settings. But overall, the results from the cross-validation also support the statement that the forest model performs well on all stations being either the best or among the best performing methods at the majority of stations.
Moreover, it can be concluded that Axams is an observation station without any unusual features that would lead to outstanding performances of any of the methods. Therefore, it is a reasonable choice as a representative for all 95 station. Examples for stations where the forest model performs better or worse can be found easily, however, in general the methods perform similarly as for station Axams.
